<!--
%\VignetteEngine{knitr::docco_linear}
%\VignetteIndexEntry{R Markdown with the Docco Linear Style}
-->

# Not Preface

R is now a <span style="color:red">large community</span>. Today we have ~~4,567~~ 6,139 R packages. My attempt here is to jot down the code snippets  based on the newer packages (by following [table of available packages, sorted by date of publication](http://cran.r-project.org/web/packages/available_packages_by_date.html)). 

***

The chunk of the codes will be taken either from the Vignette or from the main package documentation pdf. I also like to include [stack overflow threads](http://stackoverflow.com/questions/tagged/r) if there are interesting questions. These interesting and easy-to-apply codes will be applied to different data sets to develop models and assumptions. 




### Packages

Packages used in this post are:

> pander, DT, data.table 

#### pander

1. [Package pdf](http://cran.r-project.org/web/packages/pander/pander.pdf).
2. [Github](http://rapporter.github.io/pander/)
3. Last updated: 2014-XX-XX

```{r}
library(pander)
pandoc.table(mtcars[1:3, 1:4])
```


```{r}
pandoc.table(mtcars[1:2, ], style = "grid", caption = "Hello caption!")
```


```{r}
pander(prcomp(USArrests))
```


```{r}
counts <- c(18, 17, 15, 20, 10, 20, 25, 13, 12)
outcome <- gl(3, 1, 9)
treatment <- gl(3, 3)
m <- glm(counts ~ outcome + treatment, family = poisson())
```


#### DT

1. [jQuery DataTables](http://cran.r-project.org/web/packages/knitr/vignettes/datatables.html).
2. [DT Github Repo.](https://github.com/rstudio/DT)
3. [Rpubs 1: knitr ã¨ DataTables](http://rpubs.com/holidayworking/knitr_and_datatables)
4. [Rpubs 2: countrycode](http://rpubs.com/muuankarski/52544)


DT package is not on CRAN yet, and you can install it with devtools. Need to do following:

> install.packages("devtools")

> library(devtools)

> devtools::install_github('rstudio/DT')


```{r echo=FALSE}
setwd("/Users/subasishdas1/Copy/Rpubs")
library(DT)
data <- read.csv("aa.csv")
datatable(data)
```

#### data.table

1. [Package pdf](http://cran.r-project.org/web/packages/data.table/data.table.pdf).
2. [DATA ANALYSIS THE DATA.TABLE WAY](ww.datacamp.com/courses/data-analysis-the-data-table-way)

```{r}
library(data.table)
DF = data.frame(x=rep(c("a","b","c"),each=3), y=c(1,3,6), v=1:9)
DT = data.table(x=rep(c("a","b","c"),each=3), y=c(1,3,6), v=1:9)
DF
DT
```

```{r}
data(mtcars)
head(mtcars)
mtcars.dt <- data.table(mtcars)
head(mtcars.dt)

mtcars.dt1 <- data.table(mtcars, keep.rownames = TRUE)
head(mtcars.dt1)
```




That's all for this docco. :)